---
title: "Task 7: Lab 3"
author: "Hunter DeVoe"
date: "`r Sys.Date()`"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. In the case below we use the `selectInput` function to create the input widget used to drive the plot.

There are other widgets we can make!!

Notice that there are essentially only two parts

 1. Input (Controls)
 2. Render (Often a plot)

```{r slr, echo=FALSE}
library(ggplot2)
# DATA
spruce = read.csv("SPRUCE.csv")

# INPUTS
inputPanel(
  selectInput("plotg", "Choose plot type",
      list(`points` = c("Points", "Segments", "Linear Regression", "Full")
      )
    )
)

renderPlot({
  
 Points = ggplot(spruce, aes(x=BHDiameter,y=Height,color=BHDiameter)) + geom_point() + ggtitle("Height Vs BHDiameter          Hunter DeVoe")
 
 Segments = Points + geom_line()
 
 LinearRegression = Points + geom_smooth(method = "lm")
 
 Full = ggplot(spruce, aes(x=BHDiameter,y=Height,color=BHDiameter)) + geom_point() + geom_line() + geom_smooth(method="lm") + ggtitle("Height Vs BHDiameter          Hunter DeVoe")
 
 if(input$plotg == "Points") print(Points)
 
 if(input$plotg == "Segments")   print(Segments)
 
 if(input$plotg == "Linear Regression")   print(LinearRegression)
 
 if(input$plotg == "Full")   print(Full)
})
```
